---
title: "Homework7"
output: github_document
author: "Yamei Li, Meirou Guan, Tamires Amorim,Carol-Ann Jackson,"
---
```{r}
load("/Users/yameili/Desktop/ecob2000_lecture1/NHIS_2014.RData")
attach(data_use1)
max(AGE_P)
use_varb <- (AGE_P >= 25) & (AGE_P <= 55)
dat_use <- subset(data_use1,use_varb) # 
detach()
attach(dat_use)
```

```{r}
str(dat_use)
earn_lastyr <- as.factor(ERNYR_P)
str(earn_lastyr)
```
```{r}
levels(earn_lastyr) <- c("0","$01-$4999","$5000-$9999","$10000-$14999","$15000-$19999","$20000-$24999","$25000-$34999","$35000-$44999","$45000-$54999","$55000-$64999","$65000-$74999","$75000 and over",NA,NA,NA)
summary(earn_lastyr)
```
Here we are looking into the insurance coverage as dependent variable, and age, gender, race, education, marital status and region as the explanatory variables for the insurance coverage.
```{r}
model_logit1 <- glm(NOTCOV ~ AGE_P + I(AGE_P^2) + female + AfAm + Asian + RaceOther  
                    + Hispanic + educ_hs + educ_smcoll + educ_as + educ_bach + educ_adv 
                    + married + widowed + divorc_sep + veteran_stat + REGION + region_born,
                    family = binomial, data = dat_use)
model_logit1
```

For the simple linear regression (glm function) it is not necessary to set the variables in a data frame. Although for the new models we are using it will be necessary. Below is the data frame with the list of variables set to have the same number of rows with unique row names in the class “data.frame”. Because it includes a matrix it will force the columns names to have unique results.
```{r}
d_region <- data.frame(model.matrix(~ dat_use$REGION))
d_region_born <- data.frame(model.matrix(~ factor(dat_use$region_born)))  # snips any with zero in the subgroup
dat_for_analysis_sub <- data.frame(
  dat_use$NOTCOV,
  dat_use$AGE_P,
  dat_use$female,
  dat_use$AfAm,
  dat_use$Asian,
  dat_use$RaceOther,
  dat_use$Hispanic,
  dat_use$educ_hs,
  dat_use$educ_smcoll,
  dat_use$educ_as,
  dat_use$educ_bach,
  dat_use$educ_adv,
  dat_use$married,
  dat_use$widowed,
  dat_use$divorc_sep,
  d_region[,2:4],
  d_region_born[,2:12])
```

```{r}
names(dat_for_analysis_sub) <- c("NOTCOV",
                                 "Age",
                                 "female",
                                 "AfAm",
                                 "Asian",
                                 "RaceOther",
                                 "Hispanic",
                                 "educ_hs",
                                 "educ_smcoll",
                                 "educ_as",
                                 "educ_bach",
                                 "educ_adv",
                                 "married",
                                 "widowed",
                                 "divorc_sep",
                                 "Region.Midwest",
                                 "Region.South",
                                 "Region.West",
                                 "born.Mex.CentAm.Carib",
                                 "born.S.Am",
                                 "born.Eur",
                                 "born.f.USSR",
                                 "born.Africa",
                                 "born.MidE",
                                 "born.India.subc",
                                 "born.Asia",
                                 "born.SE.Asia",
                                 "born.elsewhere",
                                 "born.unknown")
```

The goal here is to keep the regression parameters in a similar scale, and ensure that the intercept represents the corrected mean, this way the output of the regression will be easier to interpret.Following, we split into training and test sets, 
```{r}
library(standardize)
set.seed(654321)
NN <- length(dat_for_analysis_sub$NOTCOV)
# restrict_1 <- as.logical(round(runif(NN,min=0,max=0.6))) # use fraction as training data
restrict_1 <- (runif(NN) < 0.1) # use 10% as training data
summary(restrict_1)
dat_train <- subset(dat_for_analysis_sub, restrict_1)
dat_test <- subset(dat_for_analysis_sub, !restrict_1)
sobj <- standardize(NOTCOV ~ Age + female + AfAm + Asian + RaceOther + Hispanic + 
                      educ_hs + educ_smcoll + educ_as + educ_bach + educ_adv + 
                      married + widowed + divorc_sep + 
                      Region.Midwest + Region.South + Region.West + 
                      born.Mex.CentAm.Carib + born.S.Am + born.Eur + born.f.USSR + 
                      born.Africa + born.MidE + born.India.subc + born.Asia + 
                      born.SE.Asia + born.elsewhere + born.unknown, dat_train, family = binomial)

s_dat_test <- predict(sobj, dat_test)


```

The goal with this model is to understand how to call the standardized objects from above and interpret the results with the “traditional model” of linear regression. The lm function.
```{r}
model_lpm1 <- lm(sobj$formula, data = sobj$data)
summary(model_lpm1)
pred_vals_lpm <- predict(model_lpm1, s_dat_test)
pred_model_lpm1 <- (pred_vals_lpm > 0.5)
table(pred = pred_model_lpm1, true = dat_test$NOTCOV)

```
```{r}
summary(sobj$data)
```

```{r}
model_logit1 <- glm(sobj$formula, family = binomial, data = sobj$data)
summary(model_logit1)
pred_vals <- predict(model_logit1, s_dat_test, type = "response")
pred_model_logit1 <- (pred_vals > 0.5)
table(pred = pred_model_logit1, true = dat_test$NOTCOV)
```
```{r}
library(e1071)
# tuned_parameters <- tune.svm(as.factor(NOTCOV) ~ ., data = sobj$data, gamma = 10^(-3:0), cost = 10^(-2:1)) 
# summary(tuned_parameters)
# figure best parameters and input into next
svm.model <- svm(as.factor(NOTCOV) ~ ., data = sobj$data, cost = 10, gamma = 0.1)
svm.pred <- predict(svm.model, s_dat_test)
table(pred = svm.pred, true = dat_test$NOTCOV)
```
```{r}
#LOSSO
x_varb <- cbind(AGE_P,I(AGE_P^2), female, AfAm, Asian , RaceOther, Hispanic, educ_hs, educ_smcoll, educ_as, educ_bach, educ_adv, married, widowed, divorc_sep, veteran_stat, REGION, region_born)
stand_Z <- function(X) {
rval <- matrix(data = NA, nrow = nrow(X), ncol = ncol(X))
for(j in 1:ncol(X)) rval[,j] <- (X[,j] - mean(X[,j]))/sd(X[,j])
return(rval)
}
x_varb_dm <- stand_Z(x_varb)
dimnames(x_varb_dm) <- dimnames(x_varb)
library(lars)
model_lars <- lars(x_varb_dm,NOTCOV)
summary(model_lars)
plot(model_lars)
coef(model_lars)
```
```{r}
library('rpart')
# tree model 
modeltree <- rpart(NOTCOV ~ AGE_P + I(AGE_P^2) + female + AfAm + Asian + RaceOther  
                    + Hispanic + educ_hs + educ_smcoll + educ_as + educ_bach + educ_adv 
                    + married+ widowed + divorc_sep + veteran_stat + REGION + region_born,data = dat_use, method = "class")
summary(modeltree)
post(modeltree, file = "tree_1.ps",
title = "Classification Tree for Health Insurance")
```
```{r}
library(glmnet)
model1_elasticnet <-  glmnet(as.matrix(sobj$data[,-1]),sobj$data$NOTCOV) 
# default is alpha = 1, lasso

par(mar=c(4.5,4.5,1,4))
plot(model1_elasticnet)
vnat=coef(model1_elasticnet)
vnat=vnat[-1,ncol(vnat)] # remove the intercept, and get the coefficients at the end of the path
axis(4, at=vnat,line=-.5,label=names(sobj$data[,-1]),las=1,tick=FALSE, cex.axis=0.5) 

plot(model1_elasticnet, xvar = "lambda")
plot(model1_elasticnet, xvar = "dev", label = TRUE)
print(model1_elasticnet)
```
lm model:
pred        0     1
  FALSE 32940  6631
  TRUE    742  1264
logit model:
 pred        0     1
  FALSE 32574  6342
  TRUE   1108  1553
svm model:
  pred     0     1
   0 32008  6095
   1  1674  1800
these three models, for the first one, the mis-classified is equal to (6631+742)/(32940+6631+742+1264)=0.177.
for the second one, the mis-classified is equal to (6342+1108)/(32574+1553+6342+1108)=0.179
for the third one, the mis-classified is equal to (6095+1674)/(32008+1800+6095+1674)=0.187

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
